---
title: "Manner predicting using Machine Learning"
author: "LiuBo"
date: "6/18/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Summary
This is a course project about practical machine learning, The goal of your project is to predict the manner using the dataset. 

I built your model, 

how you used cross validation, 

what you think the expected out of sample error is, and why you made the choices you did. 

You will also use your prediction model to predict 20 different test cases.

## Load data
The data for this project come from this source: http://groupware.les.inf.puc-rio.br/har        
First, load in the train data and test data.
```{r load data}
Train_Data <- read.csv('pml-training.csv')
Test_Data <- read.csv('pml-testing.csv')
dim(Train_Data)
dim(Test_Data)
```
There are 160 variables, and we will predict the "classe" variable which represent the Participants' manner. 

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
