---
title: "Manner predicting using Machine Learning"
author: "LiuBo"
date: "6/18/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Summary
This is a course project about practical machine learning, The goal of your project is to predict the manner using the dataset. 

I built your model, 

how you used cross validation, 

what you think the expected out of sample error is, and why you made the choices you did. 

You will also use your prediction model to predict 20 different test cases.


### Introduction
Using devices such as Jawbone Up, Nike FuelBand, and Fitbit it is now possible to collect a large amount of data about personal activity relatively inexpensively. These type of devices are part of the quantified self movement Â– a group of enthusiasts who take measurements about themselves regularly to improve their health, to find patterns in their behavior, or because they are tech geeks.

One thing that people regularly do is quantify how much of a particular activity they do, but they rarely quantify how well they do it. In this data set, the participants were asked to perform barbell lifts correctly and incorrectly in 5 different ways. More information is available from the website here: http://groupware.les.inf.puc-rio.br/har (see the section on the Weight Lifting Exercise Dataset).

In this project, the goal will be to use data from accelerometers on the belt, forearm, arm, and dumbell of 6 participants toto predict the manner in which praticipants did the exercise.

The dependent variable or response is the “classe” variable in the training set.

### Loading Data
The data for this project come from this source: http://groupware.les.inf.puc-rio.br/har        
Load the train data and test data.
```{r load data}
setwd('/Users/freefrog/Studing/DataScience/Practical_ML')

Train_Data <- read.csv('pml-training.csv',na.strings=c("", "NA", "NULL"))
Test_Data <- read.csv('pml-testing.csv', na.strings=c("", "NA", "NULL"))

dim(Train_Data);dim(Test_Data)
```
There are 160 variables, and we will predict the "classe" variable which represent the Participants' manner. 

### Cleaning the Data
In this section, we will remove variables that   
- Have too many NA values.      
- Unrelated variables. (Since the testing dataset has no time-dependence, these values are useless).   
- Low variance variables.
- Highly correlated variables.
``` {r subset data}
# Remove variables that contain NA values
Training <- Train_Data[,colSums(is.na(Train_Data))==0]
dim(Training)

# Remove unrelated variables
remove = c('X', 'user_name', 'raw_timestamp_part_1', 'raw_timestamp_part_2', 'cvtd_timestamp', 'new_window', 'num_window')
Training <- Training[,-which(names(Training) %in% remove)]
dim(Training)

# Remove low variance variables
library(caret)
zeroVar= nearZeroVar(Training[,sapply(Training, is.numeric)],
                     saveMetrics = TRUE)
Training = Training[,zeroVar[, 'nzv']==0]
dim(Training)

# Remove highly correlated variables (90%)
corrMatrix <- cor(Training[sapply(Training, is.numeric)])

corrDF <- expand.grid(row = 1:dim(corrMatrix)[1], 
                      col = 1:dim(corrMatrix)[2])
corrDF$correlation <- as.vector(corrMatrix)
levelplot(correlation ~ row+ col, corrDF)

High_cor_var = findCorrelation(corrMatrix, 
                   cutoff = .90, 
                   verbose = TRUE)
Training = Training[, -High_cor_var]
dim(Training)
```

### Split data
Then split the training data into Training and Testing data. 
```{r split data, eval = FALSE}
library(caret)

inTrain <- createDataPartition(y=Train_Data$classe, p=0.6, list=FALSE)

Training_Data <- Train_Dt[inTrain,]
Testing_Data <- Train_Dt[-inTrain,]

dim(Training_Data);dim(Testing_Data)
```

## Fitting the Model
### Decision Tree Model
```{r}
library(tree)
set.seed(12345)
Model_Tree=tree(classe~.,data=Training_Data)
summary(Model_Tree)
```

















## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
